Temporal Evolution of Erosion in Pore-Networks:\\ From Homogenization to Instability

### 2022-04-12 CL/CLResponse2.tex
BeforePublication

\newcommand{\EM}[1]{\noindent \color{cyan} (EM: #1)\normalcolor}
\newcommand{\KB}[1]{{\color{red}{Katia: #1}}}
\newcommand{\del}[1]{\noindent \color{red} \st{#1}\normalcolor}

@@

\opening{Dear Editor,}

@@

The main changes to our manuscript include:
%
\begin{itemize}
    \item Generalization of the results for an arbitrary erosion law.
    \item Identifying the transition condition between homogenization and channelization for a general erosion law.
    \item Showing the prediction power of our local dynamics model for a nonlinear erosion model.
    \item Showing robustness of the phase transition to boundary condition changes and thresholding effects.
\end{itemize}

@@

\end{document}
in

>>>>

\newcommand{\EM}[1]{\noindent \color{cyan} (EM: #1)\normalcolor}
\newcommand{\KB}[1]{{\color{red}{Katia: #1}}}
\newcommand{\del}[1]{\noindent \color{red} \st{#1}\normalcolor}
\newcommand{\add}[1]{\noindent \color{blue} #1 \normalcolor}

@@

\opening{Dear Editor,}
\add{
We would like to thank for reviewers' careful reading and valuable comments. We appreciate that our revised work ``Temporal Evolution of Erosion in Pore-Networks: From Homogenization to Instability'' was found  ``greatly improved'', ``to achieve the level of significance that it can be published PRL'' and ``is a substantial advance in the field''. The remaining most significant concern expressed by all reviewers is a convincing experiment test that our theory can directly apply to. Unfortunately our group is a theory group and lack of lab space. 
}

@@

The main changes to our manuscript include:
%
\add{
\begin{itemize}
    \item Acknowledging and discussion of the limitations of the general erosion law.

\end{itemize}
}

@@

\end{document}
